Raft Distributed Consensus Algorithm over\\ WebRTC (Web Real-Time Communication)

### 2015-09-19 research_class/paper.tex
Build full and minimal versions.
- WebRTC citations in full version.

@@

There is a large suite of protocols that are required for a working
WebRTC system. The Internet Engineering Task Force (IETF) organization
is responsible for specifying and/or standardizing (where necessary)
the protocols that are part of WebRTC. In many cases an existing
protocol is applicable and is referenced or extended as part of the
WebRTC suite. %TODO/CITE

@@

\begin{enumerate}
    \item data transport
    \item data framing and security
    \item connection management
    \item data formats
    \item presentation and control
    \item local system support functions
\end{enumerate}

The last three functionality groups focus on interactive audio and video
applications and are less relevant to Raft over WebRTC. The WebRTC
section of the bibliography %TODO: reference link
has a (partial) list of WebRTC specific protocol drafts and other
related protocol standards for the first three functionality groups.

@@

@@

>>>>

%% Configure which sections are included:
%\newcommand*{\OPTIONAL}{}

@@

There is a large suite of protocols that are required for a working
WebRTC system. The Internet Engineering Task Force (IETF) organization
is responsible for specifying and/or standardizing (where necessary)
the protocols that are part of WebRTC \cite{draft-rtcweb-overview}
\cite{draft-rtcweb-security-arch} \cite{draft-rtcweb-security}. In many
cases an existing protocol is applicable and is referenced or
extended as part of the WebRTC suite. %TODO/CITE

@@

\begin{enumerate}
    \item data transport
        \ifdefined\OPTIONAL
        \\
        \cite{draft-rtcweb-transports}
        \cite{draft-rtcweb-qos}
        \cite{RFC4960:sctp}
        \cite{RFC3758:sctp-reliability}
        \cite{draft-sctp-dtls-encaps}
        \cite{draft-mmusic-sctp-sdp}
        \cite{draft-sctp-ndata}
        \cite{draft-rtcweb-rtp-usage}
        \cite{draft-rtcweb-data-channel}
        \cite{draft-rtcweb-data-protocol}
        \cite{draft-rtcweb-alpn}
        \cite{RFC5245:ice}
        \cite{RFC5128:p2p-nat}
        \cite{RFC5389:stun}
        \cite{RFC3489:stun-udp}
        \cite{RFC5766:turn}
        \cite{RFC6156:turn-ipv6}
        \cite{RFC6544:tcp-ice}
        \cite{RFC4571:rtp-rtcp}
        \cite{RFC5764:dtls-srtp}
        \fi
    \item data framing and security
        \ifdefined\OPTIONAL
        \\
        \cite{RFC3550:rtp}
        \cite{RFC3711:srtp}
        \cite{draft-rtcweb-rtp-usage}
        \cite{draft-rtcweb-data-channel}
        \cite{draft-rtcweb-data-protocol}
        \fi
    \item connection management
        \ifdefined\OPTIONAL
        \\
        \cite{RFC2327:sdp}
        \cite{RFC3264:sdp-offer-answer}
        \cite{draft-rtcweb-jsep}
        \cite{RFC5245:ice}
        \cite{draft-mmusic-trickle-ice}
        \cite{RFC5763:srtp-using-dtls}
        \fi
    \item data formats
    \item presentation and control
    \item local system support functions
\end{enumerate}

The last three functionality groups focus on interactive audio and video
applications and are less relevant to Raft over WebRTC. \ifdefined\OPTIONAL
Some of the important standards for the first three functionality
groups are cited above. \fi

@@

\ifdefined\OPTIONAL

@@

\fi  % \ifdefined\OPTIONAL
